Object-Oriented Internet - Azure Interoperability

### 2020-11-07 Latex/Manuscript.pandoc.tex
Work out Markdown\60.GatewayImplementation.md #35
- integrate with other sections

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

@@

From the M2M communication concept, a broader concept of a smart factory
can be derived. In this concept, the mentioned robots are only executive
assets of an integrated supervisory control system responsible for macro
optimization of an industrial process composed into one whole.
Deployment of the smart factory concept requires a hybrid solution and
interoperability of the mentioned above heterogeneous environments. This
approach is called the fourth industrial revolution and coined as
Industry 4.0. It is worth stressing that machines - or more general
assets - interconnection is not enough, and additionally, assets
interoperability has to be expected for the deployment of this concept.
In this case, muli-vendor integration makes communication
standardization especially important, namely it is required that the
payload of the message is standardized to be factored on the gathering
site and consumed on the ultimate destination site.

@@

\hypertarget{ooi-main-technology-features}{%
\section{OOI Main Technology
Features}\label{ooi-main-technology-features}}

\begin{itemize}
\tightlist
\item
  Machinie To Machine communication based on the semantic data
\item
  OOI PubSub Implementation Architecture
\item
  Simple, complex and structural data processing
\end{itemize}

@@

Mobile data fetching is related to variety of last mile communication
technologies, for example RFID, WI-FI, VHF, etc. Subscription could be
supported using messaging systems, e.g.~AMQP. A good candidate to
leverage consumption is OPC Unified Architecture.

@@

\begin{itemize}
\tightlist
\item
  the mobile data must be sent over the Internet using messages;
\item
  the payload of these messages is consumed by an OPC Server responsible
  to expose it in the Address Space;
\item
  the application as an OPC UA client consumes the exposed data and
  generates revenue for the end-user.The phrase ``Internet of Things''
  started its life as the title of a presentation made in 1999 and aimed
  at explaining a new idea of radio frequency identification (RFID) in
  the context of the supply chain performance. It is clear that it
  doesn't mean that someone has any right to control how others use the
  phrase, but my point is that a precise term definition is important
  for working together on: common rules, architecture, solutions,
  requirements, capabilities, limitations, etc. In practice having a
  common definition it is possible to check a selected technology,
  solution or product capabilities against requirements of the
  application entitled to use this term.
\end{itemize}

@@

Internet of Things is all about:

\begin{itemize}
\tightlist
\item
  mobile data fetching -- how to gather the data from mobile devices
  (things);
\item
  mobile data subscription -- how to transfer the data over the Internet
  to a place where it could be processed;
\item
  mobile data processing -- how to integrate the data into a selected
  application to improve process behavioral performance.
\end{itemize}

Data fetching is related to a variety of last mile communication
technologies, for example RFID, WI-FI, VHF, Bluetooth, etc. Subscription
could be supported using messaging systems, e.g.~AMQP, MQTT, etc. A good
candidate for leveraging data consumption is for example OPC Unified
Architecture.

\hypertarget{azure-to-sensors-a2s-connectivity-deployment-field-level-connectivity}{%
\section{Azure to Sensors (A2S) connectivity deployment (field level
connectivity)}\label{azure-to-sensors-a2s-connectivity-deployment-field-level-connectivity}}

\begin{quote}
The title must be revised
\end{quote}

\begin{itemize}
\tightlist
\item
  \textbf{Architecture} - Domain model presenting relationship between
  the: Azure, PubSub Gateway, Device, Design and development tools
\item
  \textbf{Connectivity} - Describe reactive nature of the Azure
  monitoring process data (telemetry) services.
\item
  \textbf{Deployment phases}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\newenvironment{Shaded}{}{}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{#1}}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.49,0.56,0.16}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.53,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.56,0.13,0.00}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.73,0.13,0.13}{\textit{#1}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.02,0.16,0.49}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.40,0.40,0.40}{#1}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.74,0.48,0.00}{#1}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.73,0.40,0.53}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.10,0.09,0.49}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{#1}}}}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

@@

From the M2M communication concept, a broader concept of a smart factory
can be derived. In this concept, the mentioned robots are only executive
assets of an integrated supervisory control system responsible for macro
optimization of an industrial process composed into one whole.
Deployment of the smart factory concept requires a hybrid solution and
interconnection of the mentioned above heterogeneous environments. This
approach is called the fourth industrial revolution and coined as
Industry 4.0. It is worth stressing that machines - or more general
assets - interconnection is not enough, and additionally, assets
interoperability has to be expected for the deployment of this concept.
In this case, muli-vendor integration makes communication
standardization especially important, namely it is required that the
payload of the message is standardized to be factored on the gathering
site and consumed on the ultimate destination site.

@@

\hypertarget{reactive-machine-to-machine-communication-state-of-the-art}{%
\section{Reactive Machine to Machine communication state of the
art}\label{reactive-machine-to-machine-communication-state-of-the-art}}

\hypertarget{opc-ua-pubsub-main-technology-features}{%
\subsection{OPC UA PubSub Main Technology
Features}\label{opc-ua-pubsub-main-technology-features}}

\hypertarget{ooi-main-technology-features}{%
\subsection{OOI Main Technology
Features}\label{ooi-main-technology-features}}

To address multi-vendor environment a standard solution is required.
=\textgreater{} PubSub. The specyfication is abstrack, so concrete
oimplementation has been selected OOI.

\begin{itemize}
\tightlist
\item
  Protocol stack
\item
  DataTypes binary and JSON encoding
\item
  Data Transfer Object embedded in the NetworkMessage
\end{itemize}

\hypertarget{problem}{%
\subsection{Problem}\label{problem}}

As stated in Sec. 1 the interoperability of the \textbf{machine-centric}
cyber-physical systems and \textbf{human-centric} cloud-based front-end
can be implemented applying one of the following scenarios:

\begin{itemize}
\tightlist
\item
  \textbf{direct interconnection} - cloud-based dedicated communication
  services allow to attach it to the cyber-physical system making up a
  consistent M2M communication network using its protocol stack
\item
  \textbf{gateway based interconnection} - native build-in communication
  services allows attaching the cloud to the cyber-physical system using
  an out-of-bound protocol stack
\end{itemize}

By design, the direct approach requires that the cloud has to be
compliant with the interoperability standard the cyber-physical system
uses. As a result, it becomes a consistent part of the cyber-physical
system.

Data models, roles, and responsibility differences of both solutions
make this approach imposable or impractical in typical cases.

how to interconnect two completely different environment:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  machine-centric reactive interoperability addressing real-time mobile
  applications
\item
  human-centric interactive web based user graphical interface
\end{enumerate}

\hypertarget{architecture-scenarios}{%
\subsection{Architecture scenarios}\label{architecture-scenarios}}

\begin{itemize}
\tightlist
\item
  tightly coupled - treat Azure as tightly coupled communication part of
  the m2m
\item
  loosely coupled - use gateway as the intensional man in the middle
\end{itemize}

\hypertarget{requirements}{%
\subsection{Requirements}\label{requirements}}

\begin{itemize}
\tightlist
\item
  standard base
\item
  reactive interoperability (sessionless)
\item
  gateway architecture

  \begin{itemize}
  \tightlist
  \item
    gateway is part of the M2M communication network (in-baud )
  \item
    out-of-band communication - asynchronous data exchange
  \item
    semantic-context integration (types mapping)
  \item
    security context independency
  \item
    separation of concerns - composable implementation
  \end{itemize}
\end{itemize}

\hypertarget{library-selection-against-the-problem}{%
\subsection{Library selection against the
problem}\label{library-selection-against-the-problem}}

It is real a The defined in sec.~problem is engineering challenge is how
to interconnect two completely different environment:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  machine centric reactive interoperability addressing real-time mobile
  applications
\item
  human centric interactive web based user graphical interface
\end{enumerate}

Why reactive interoperability

\begin{itemize}
\tightlist
\item
  data mobility
\item
  network trafik asymmetry
\item
  serverless implementation (self contained implementation)
\end{itemize}

\hypertarget{sessionless}{%
\subsection{Sessionless}\label{sessionless}}

\begin{itemize}
\tightlist
\item
  Without a session; taking the form of a series of isolated requests.
\item
  System having virtual session manager used sessionless-oriented
  protocol to communicate with user device via wireless channel and
  session-oriented protocol to communicate with host server
\end{itemize}

\hypertarget{library-description-targeting-reactive-interoperability}{%
\subsection{Library description targeting reactive
interoperability}\label{library-description-targeting-reactive-interoperability}}

In Fig. fig\_archit a generic architecture of the Machine to Machine
(M2M) interoperability is presented. A detailed description of this
model is covered by \cite{RefWorks:doc:5d6cdbbbe4b082ad50f3a83e}, but in
this section, the most important features of this model have been
abstracted to settle a foundation for further discussion related to
systematic design, development, and deployment of the mobile
applications compliant with the more general IoT concept. The main aim
is the examination of how the model addresses challenges defined in
Section \ref*{sec.intro}.

\hypertarget{mobility}{%
\subsection{Mobility}\label{mobility}}

For any generic solution addressing the development and deployment of
the cyber-physical system the data holder mobility behavior must be
considered apart from the described above features. Mobile data means
that it may come from mobile devices or be generated in unpredictable
attachment points.

If the data origin holding asset is a mobile device it means that we
must deal with the dynamic Internet attachment point. A typical example
of this scenario is portable monitoring or control of the underlying
process, for example, a portable healthcare solution. Another scenario
is ad hoc interconnected data holder assets, for example, cars entering
a service area.

In case the generation places of data are arbitrary it means that the
data appearance must be recognized and processed as an event. A good
example of this scenario is a product (e.g.\textasciitilde hygiene
products, cosmetics, drugs, cars, cigarettes) global tracking system -
an application domain where the Internet of Things (IoT) term has been
coined
\cite{RefWorks:doc:5d87d1c9e4b0bc72a68d7b46, RefWorks:doc:5d87d02be4b0e88bdacab9a7}.
In this context, the IoT is all about:

\begin{itemize}
\tightlist
\item
  \textbf{mobile data fetching} - how to gather data from mobile things
  (data holder assets)
\item
  \textbf{mobile data distribution} - how to transfer the data over the
  Internet to all places where it could be processed
\item
  \textbf{mobile data processing} - how to integrate consistently the
  partial data into a selected application as one whole to improve
  selected process performance
\end{itemize}

One of the arguments for the Internet of Things is allowing distributed
yet interlinked devices, machines, and objects (data holders) to
interact with each other without relying on human interaction to set-up
and commission the embedded intelligence.

In case any kind of mobility has to be considered the next engineering
challenge is dynamic discoverability on the network and the possibility
of establishing semantic and security context of the parts composing the
cyber-physical distributed application.

\begin{itemize}
\tightlist
\item
  Machine To Machine communication based on the semantic-data
\item
  OOI PubSub Implementation Architecture
\item
  Simple, complex and structural data processing
\end{itemize}

@@

@@

\begin{itemize}
\tightlist
\item
  the mobile data must be sent over the Internet using messages;
\item
  the payload of these messages is consumed by a ultimate destination
  responsible to process it according to the solution scenario,
  e.g.~displacing recovered data using web UI
\item
  the application as an OPC UA client consumes the exposed data and
  generates revenue for the end-user.
\end{itemize}

The phrase ``Internet of Things'' started its life as the title of a
presentation made in 1999 and aimed at explaining a new idea of radio
frequency identification (RFID) in the context of the supply chain
performance. It is clear that it doesn't mean that someone has any right
to control how others use the phrase, but my point is that a precise
term definition is important for working together on: common rules,
architecture, solutions, requirements, capabilities, limitations, etc.
In practice having a common definition it is possible to check a
selected technology, solution or product capabilities against
requirements of the application entitled to use this term.

@@

\hypertarget{from-ooi-ri-mpostolmanuscript.tex}{%
\subsection{from
OOI-RI-MPostolManuscript.tex}\label{from-ooi-ri-mpostolmanuscript.tex}}

\hypertarget{reactive-interoperability-implementation}{%
\subsubsection{Reactive Interoperability
Implementation}\label{reactive-interoperability-implementation}}

This section covers an analysis of how to use the proposed domain model
\texttt{\textbackslash{}cite\{mpostol2020\}} to make strategic design
decisions and distribute functionality to reusable loosely coupled parts
using the dependency injection software engineering and adaptive
programming using the approach proposed in
\texttt{\textbackslash{}cite\{RefWorks:doc:5d9796cbe4b0f66c52dccf04\}}.

The \textbf{Reactive Interoperability} concept has been implemented as
an open-source library named \texttt{SemanticData} in the project
Object-Oriented Internet \cite{RefWorks:doc:5c66740ae4b081adf5804596}
designed to be a foundation for developing application programs that are
taking part in the message-centric communication pattern. From the above
discussion, we can learn that the main design decisions must concern
standardization and flexibility. Standardization needs the selection of
an international interoperability specification to make the library
ready to be adopted by the multi-vendor environment. Flexibility
requires an architecture that promotes the polymorphic independent
implementation of essential functions.

Piece by piece integration of a cyber-physical system using multi-vendor
products requires that M2M communication employs international standards
as the interoperability foundation. Following the presented conclusions,
OPC Unified Architecture Part 14 PubSub
\cite{RefWorks:doc:5d98837de4b055984c0eecf0} is selected in this
respect. By design, this standard supports the required
publisher-subscriber communication pattern. It must be stressed that by
design it provides only an abstract specification. Abstract means that
the standard must not limit the implementation strategy. This
relationship shall be recognized as the proof of concept to verify that
the implementation of the proposed model is feasible to be compliant
with the selected standard as envisioned and open to support all
functionality required to establish the interoperability context.

For many parts of the \textbf{Reactive Application} domain model (Sect.
\ref*{sec.DomainModel}) a polymorphic approach to implementation is
required. To promote the polymorphic ready solution the following
concepts have been adopted:

\begin{itemize}
\tightlist
\item
  \texttt{separation\ of\ concerns} - to allow an independent
  development of the parts \cite{RefWorks:doc:5d92609be4b02eb43d372bd1},
\item
  \texttt{dependency\ injection} - to allow late binding of separately
  implemented parts \cite{RefWorks:doc:5d925b77e4b030b4e0596f5d}.
\end{itemize}

In Fig. the implementation architecture of the \textbf{Reactive
Application} is proposed. The common functionality has been implemented
as the Software Development Kit (SDK) available as the NuGet package
\texttt{\textbackslash{}cite\{RefWorks:doc:5c66740ae4b081adf5804596\}}.
To promote the polymorphic approach, it has the factory class
\texttt{DataManagementSetup} that is a placeholder to gather all
injection points used to compose external parts. To be injected the
parts must be compliant with appropriate contracts expressed as the
following interfaces representing the following functionality:

\begin{itemize}
\tightlist
\item
  \texttt{IBindingFactory} - bidirectional data exchange with the
  underlying process,
\item
  \texttt{IConfigurationDataFactory} - the configuration data access,
\item
  \texttt{IMessageHandlerFactory} - pushing the \textbf{Message}
  entities to/pulling from \emph{Distribution Channel} (Fig.
  \ref*{fig_DomainModel}),
\item
  \texttt{IEncodingFactory} - searching a dictionary containing value
  converters.
\end{itemize}

It is expected that the functionality implementation represented by
these interfaces is provided as external composable parts.

\hypertarget{process-data-access}{%
\paragraph{Process Data Access}\label{process-data-access}}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{label\{process-data-access\}}
\end{Highlighting}
\end{Shaded}

The \emph{DataRepository} represents data holding assets in the
\emph{Reactive Application} and, following the proposed architecture,
the \emph{IBindingFactory} interface is implemented by this external
part. It captures functionality responsible for accessing the process
data from \emph{LocalResources}. The \emph{LocalResources} represents an
external part that has a very broad usage purpose. For example, it may
be any kind of the process data source/destination, i.e.~\emph{Raw Data}
or \emph{Address Space Management} (Fig. \ref*{fig_archit}). By design,
the \emph{DataRepository} and associated entities,
i.e.~\emph{Local Resources}, \emph{Consumer}, \emph{Producer} have been
implemented as external parts, and consequently, the application scope
may cover practically any concern that can be separated from the core
\emph{Reactive Application} implementation.

Depending on the expected network role the library supports the external
implementation of:

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{\textbackslash{}begin}\NormalTok{\{}\ExtensionTok{itemize}\NormalTok{\}}
  \FunctionTok{\textbackslash{}item} \FunctionTok{\textbackslash{}emph}\NormalTok{\{Consumer\} - entities processing data from incoming messages,}
  \FunctionTok{\textbackslash{}item} \FunctionTok{\textbackslash{}emph}\NormalTok{\{Producer\} - entities gathering process data and populating outgoing messages.}
\KeywordTok{\textbackslash{}end}\NormalTok{\{}\ExtensionTok{itemize}\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

The \texttt{Consumer} and \texttt{Producer} parts are derived from the
\texttt{DataRepository} Fig. The \texttt{Consumer} uses the
\texttt{IBindingFactory} to gather the data recovered from the
\textbf{Message} instances pulled from the \textbf{Distribution
Channel}. The received data may be processed or driven to any data
destination. The \texttt{Producer} mirrors the \texttt{Consumer}
functionality and, after reading data from an associated source,
populates the \texttt{Message} using the gathered data.

\hypertarget{cloud-to-sensors-field-level-connectivity}{%
\section{Cloud to Sensors Field Level
Connectivity}\label{cloud-to-sensors-field-level-connectivity}}

\hypertarget{architecture}{%
\subsection{Architecture}\label{architecture}}

\hypertarget{introduction-1}{%
\subsubsection{Introduction}\label{introduction-1}}

As it was explained in Sect 1, to follow the Industry 4.0 concept a
hybrid environment integrating reactive Machine to Machine
interconnection and interactive web-based user interface is required.
The main challenge of the solution in concern is to design a generic but
reusable architecture that addresses interoperability of these diverse
interconnection scenarios ruled by different requirements, namely

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \textbf{machine-centric} machine to machine real-time mobile
  interoperability
\item
  \textbf{human-centric} cloud-based front-end
\end{enumerate}

Interconnection of the reactive \textbf{machine-centric} and interactive
\textbf{human-centric} environments can be implemented by applying one
of the following scenarios:

\begin{itemize}
\tightlist
\item
  \textbf{direct interconnection} - cloud-based dedicated communication
  services are engaged to attach it to the cyber-physical system making
  up a consistent M2M communication network using a common protocol
  stack
\item
  \textbf{gateway based interconnection} - native build-in communication
  services allows attaching the cloud to the cyber-physical system using
  an out-of-bound protocol stack
\end{itemize}

In the solution in concern, the interconnection of assets is not enough
hence their interoperability is expected. In this case, using the same
communication stack must be recognized as only a necessary condition. To
support interoperability common data understanding is required. By
design, the direct approach requires that the cloud has to be compliant
with the interoperability standard the cyber-physical system uses. As a
result, it becomes a consistent part of the cyber-physical system.
Additionally, to meet this requirement the cloud and cyber-physical
systems have to establish

\begin{itemize}
\tightlist
\item
  directly the same semantic-context
\item
  directly the same security-context
\end{itemize}

The possibility to establish a common semantic-context in the
multi-vendor environment makes communication standardization especially
important. In this case, it is required that the encoding of the payload
of messages exchanged over the network (Data Transfer Object - TDO) is
standardized so that the payload can be factored on the data-gathering
site and consumed on the ultimate destination data processing sites.
Security between the data origin and ultimate data destination refers to
the protection of messages (security-context) against malicious users.
It is required that communicating parties are using the same
cyber-security measures.

\hypertarget{why-not-direct}{%
\subsubsection{why not direct}\label{why-not-direct}}

The decision to follow the \textbf{direct interconnection} scenario must
be derived from an analysis of the capabilities of available services in
concern. However, for the development strategy of this type of solutions
this analysis can be done partially taking into account two features
that can be considered invariable:

\begin{itemize}
\tightlist
\item
  by design the cloud-based services must be virtual - they are used to
  handle many solutions at the same time
\item
  by design the M2M communication is usually constrained by the
  real-time requirements
\end{itemize}

In practice, the set of assets embedded in the cyber-physical system is
very stable. On the another hand, the virtualization of services means
that they must be very flexible to handle the attachment of new assets
proactively (acting in advance) at run time. As a result, by design, the
cloud services must be repressible to register and authenticate devices
exposing endpoints in the public network to allows the device to access
a provisioning cloud service. It requires that a session over the
Internet has to be established by the data holding asset at a
preparation step.

To meet the requirements of real-time distributed control the
cyber-physical system may use protocols applicable only to local
computer networks (e.g.~multicast IP, Ethernet, TSN, etc.). Because the
cloud services support only protocols handling interconnection over the
Internet the interaction with the cloud requires remote agents,
i.e.~agents attached locally to the M2M network implemented applying one
of the following archetypes:

\begin{itemize}
\tightlist
\item
  \textbf{edge device} - remote cloud agent acting as an intermediary
  for nodes of the cyber-physical network
\item
  \textbf{field level gateway} - a dedicated custom device acting as an
  intermediary for nodes of the cyber-physical network
\item
  \textbf{embedded gateway} - a software part composed into a selected
  node of the cyber-physical network
\end{itemize}

\textbf{Edge device} is a device that connects directly to the cloud
services but acts as an intermediary for other devices called leaf
devices. Additionally, it allows the selection of initial data
processing and execution of them using local resources. The \textbf{edge
device} may be located close to the leaf devices and attached to the
cyber-physical network using protocols applicable only to local computer
networks. In this scenario, it is possible to use a custom protocol
stack to get connected to the \textbf{edge device} with the cloud and
helps to save the bandwidth thanks to sending only the results of local
processing. In this approach, the \textbf{edge device} is part of cloud
vendor products and cannot be recognized as a generic solution that can
be used to connect to other clouds at the same time.

The \textbf{field level gateway} is also build atop of the middleware
concept. The only difference compared with the \textbf{edge device} is
necessity to use officially supported by the cloud vendor services to
get connected. In this scenario the process data may be transferred to
many clouds at the same time provided that the gateway offers this
functionality.

\begin{figure}
\centering
\includegraphics{../.Media/StrategyDomainModel.png}
\caption{Strategy Domain Model}
\end{figure}

Unlike the above described solutions, the \textbf{embedded gateway} is
not derived from the middleware concept. The domain model for this
archetype is presented in the Fig. Promoting separation of concern
design principle, the gateway functionality should be implemented as a
self-contained software part embedded in the \texttt{Networking} service
of the \texttt{Cipher-physical\ node}. Main functionality of this
component is to transfer selected data between
\texttt{Cyber-physical\ network} using \texttt{Networking} services of
an existing \texttt{Cyber-physical\ node} and
\texttt{Cloud-based\ front-end} using officially supported by the cloud
vendor interconnection services.

The \textbf{embedded gateway} archetype relaxes most of the issues
described above: cipher-physical network real-time behavior, data
encoding incompatibility, security-context differences to name only a
few. The main goal of this article is to provide proof that the
\textbf{embedded gateway} archetype implementation is possible based on
a generic architecture that can be used as a foundation for the
integration of the heterogenous environments in concern. The proposed
implementation is designed for selected interoperability standard and
cloud product.

\hypertarget{why-pubsub}{%
\subsection{Why pubsub}\label{why-pubsub}}

To comply with the Industry 4.0 communication criterion, even the lowest
category requires that the product must be addressable over the network
via TCP/UDP or IP and has to support the OPC UA Information Model. As a
result, any product being advertised as Industry 4.0 enabled must be OPC
UA-capable somehow. To support the multi-vendor environment OPC Unified
Architecture interoperability standard has been selected. OPC UA
supports the following two patterns to be used to transfer data between
communicating parties:

\begin{itemize}
\tightlist
\item
  connection-oriented: requires a session that has to be established
  before any data can be sent between sender and receiver
\item
  connectionless-oriented: the sender may start sending messages (called
  packets or datagrams) to the destination without any preceding
  handshake procedure
\end{itemize}

Using the connection-oriented communication pattern it is difficult or
even impossible to gather and process mobile data (Sec. I), which is one
of the Internet of Things paradigms. OPC UA Part 14 PubSub offers the
connectionless approach as an additional option to session based
client-server interoperability and is a consistent part of the OPC UA
specifications suit. As the result it can be recognized as the IoT ready
technology.

\begin{quote}
{[}29{]} Mariusz Postol, UA Part 14: PubSub Main Technology Features in
Object Oriented Internet, https://github.com/mpostol/OPC-UA-OOI, 2019,
DOI: 10.5281/zenodo.1198852
\end{quote}

\hypertarget{why-azure}{%
\subsection{Why Azure}\label{why-azure}}

The presented proposals in the article are backed by proof of concept
reference implementations. For this study, prototyping addresses
Microsoft Azure cloud products. There are many reasons for selecting
Azure to accomplish cloud-based front-end of CFS. Azure offers
Infrastructure as a Service (IaaS) and Platform as a Service (PaaS)
capabilities. As a result, the platform can be used not only as a
cloud-based front-end for CFS. By design, the Azure services are
compliant with Security Development Lifecycle (SDL) an industry-leading
security process. It is also compliant with the new international
standard for cloud privacy, namely ISO 27018. Solutions hosted on Azure
are scaled up to millions of users without any additional coding. For
the development of the CFS front-end, it is essential that Azure
provides very efficient storage services usefully for real-time process
data archival. Azure provides a vast variety of hybrid connections
including but not limited to virtual private networks (VPNs), caches,
content delivery networks (CDNs), ExpressRoute, and IoT dedicated
services that can be directly used to implement cloud-based front-end
for CFS. Because it is also integrated with other Microsoft tools like
Office 365, Outlook, and SharePoint using Azure allows preserving
investment and exporting process data to the mentioned tools. Azure also
offers services supporting analytics and intelligence capabilities for
further improving business processes and decision making. It is the only
cloud platform that offers Blockchain as a Service (BaaS), Machine
Learning, Bots, and Cognitive APIs capabilities.

Azure aids Internet protocols and open standards such as JSON, XML,
SOAP, REST, MQTT, AMQP, and HTTP. A software development kits for C\#,
Java, PHP, and Ruby are available for custom applications. Azure
provides services supporting data exchange over the OPC UA, but they
don't support pubsub compliant with the OPC UA Part-14. Connectivity
services on the network use JSON-based Data Transfer Object encoded
based on schema derived from the solution metadata.

More detailed description of the selected Azure features in context of
the application in concern are covered by the Sec.
\texttt{azure-main-technology-features}.

\hypertarget{why-ooi}{%
\subsection{Why OOI}\label{why-ooi}}

Based on the sessionless and session-oriented communication patterns
examination against the IoT requirements (cite mpostol 2020) it could be
concluded that the connectionless pattern better suites issues related
to the assets mobility and traffic asymmetry that is characteristic for
the application domains in concern. Additionally, to promote
interoperability and address the demands of the M2M communication in the
context of a multi-vendor environment the prototyping should use an
framework that must be compliant with the OPC UA Part 14 PubSub spec.
According to proposed architecture presented in Fig. above to implement
the \texttt{Embedded\ Gateway} as a composable part of the
\texttt{Cipher-physical\ Node} a library implementing
\texttt{Networking} functionality in compliance with mentioned above
specification is a starting point for further development. Additionally
it must be assumed that the library used to deploy
\texttt{Embedded\ Gateway} support dependency injection and be capable
to compose an external part supporting Azure/pubsub gateway
functionality. The composition process must be available without
modification of the core code of an existing library. As a result the
prototyping is to be limited to implementation of the
\texttt{Embedded\ Gateway} software part only.
